---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# waccR

`waccr` is an R package for the analysis of [Aswath Damodaran's](http://people.stern.nyu.edu/adamodar/New_Home_Page/home.htm) weighted cost of capital (WACC) [data](http://people.stern.nyu.edu/adamodar/New_Home_Page/datafile/wacc.htm). 

## installation and usage: 

```{r, eval = F}

devtools::install_github("RobertMyles/waccR")

library(waccR)

w_data <- wacc()

```

## WACC 

The Weighted Average Cost of Capital (WACC) represents the average cost of financing a
company's debt and equity. There are two approches to calculating it, one based on the "Build-up" approach, the other on the Capital Assets Pricing Model (CAPM) approach. 

$$WACC = K_e \times W_e + K_d \times W_d$$

where $K_d$ is the after-tax cost of debt, $W_e$ and $W_d$ the proportion of equity and debt in a firm based on market value, and $K_e$ is the cost of equity, which, using the CAPM approach, is calculated with:   

$$K_e = R_f + \beta(R_m) + R_s + CR + FR$$ 

where $R_f$ is risk-free rate, $R_m$ is the market premium, $Rs$ is the company size premium,
$CR$ the [country risk premium](https://github.com/RobertMyles/riscoBrasil), FR the firm-specific risk and $\beta$ is a measure of the systematic risk, usually of the industry sector, in comparison to the market as a whole.

$\beta$ for various sectors of US industry is available with:  

```{r, echo=FALSE}
library(waccR)
```
```{r}
betas()
```

For more, see Professor Damodaran's webpage: [http://people.stern.nyu.edu/adamodar/](http://people.stern.nyu.edu/adamodar/)


