---
title: "Calculate WACC in R"
author: "Robert Myles McDonnell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Calculate WACC in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The Weighted Average Cost of Capital (WACC) represents the average cost of financing a
company's debt and equity. There are two approches to calculating it, one based on the "Build-up" approach, the other on the Capital Assets Pricing Model (CAPM) approach. 

$$\text{WACC} = C_e \times E + C_d \times D$$

where $C_d$ is the after-tax cost of debt, E and D the proportion of equity and debt in a firm based on market value, and $C_e$ is the cost of equity, which, using the CAPM approach, is calculated with:   

$$C_e = R_f + \beta(R_m) + R_s + \text{Risk} + \text{Firm Risk}$$ 

where $R_f$ is risk-free rate, $R_m$ is the market premium, $R_s$ is the company size premium, *Risk* the [country risk premium](https://github.com/RobertMyles/riscoBrasil), *Firm Risk* the firm-specific risk and $\beta$ is a measure of the systematic risk, usually of the industry sector, in comparison to the market as a whole.  

According to [this](http://www.iese.edu/research/pdfs/DI-0914-E.pdf) paper, most companies do it wrong.  


`waccR` make sit *super* easy to get the data for the US:  

```{r}
library(waccR)
# WACC: 

wacc_usa <- wacc()
head(wacc_usa)

```


```{r}
# Industry Betas (US): 

betas_usa <- betas() 
head(betas_usa)
```

